openarchaeoCollaboration

### 2023-01-30 analysis/paper.qmd
Remove custom plot font
Restore variable lost in e4fb22d1b0f66a9eb0b3d91bcb5aee4c761eb3bc

```{r plot-theme}
theme_oarch <- function() theme(
  text = element_text(family = "Lato")
)
```

@@

>>>>

```{r plot-theme}
theme_oarch <- function() theme(
)
```

@@

```{r lifespan-stats}
oarch %>% 
  unnest(gh_commits) %>% 
  drop_na(datetime) %>% 
  group_by(item_name) %>%
  mutate(n_contribs = map_int(gh_contribs, vctrs::vec_size)) %>% 
  summarise(
    category = first(category),
    n_contribs = first(n_contribs),
    n = n(),
    first_commit = min(datetime),
    last_commit = max(datetime),
    lifespan = as.integer(last_commit - first_commit),
    commit_rate = n / lifespan
  ) ->
  oarch_lifespan
```
